%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{EXPERIENCE}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}
%---------------------------------------------------------
  \vspace{5mm}
  \cventrynew
    {ZURU Toys - Data Scientist} % Organisation
    {Auckland, NZ | Nov 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Promoted from Data Analytics Intern → Junior Data Scientist → Data Scientist in under 2 years.}
        \item {Owned end-to-end TikTok trend intelligence system ingesting 20k hashtags/day via exclusive API access, generating actionable insights for product, licensing, and marketing teams.}
        \item {Built automated analytics pipelines delivering daily insights at scale, while preserving human oversight for final validation and storytelling.}
        \item {Designed rising-trend detection and integrated social, search, and ecommerce signals to identify demand-aligned opportunities, informing NPD ideation and external licensing discussions.}
        \item {Insights contributed to internal decision-making, leading to 3 ZURU products being greenlit, and were adopted by major retail partners (Walmart, Target) to guide live inventory management, buying strategies, and trend-led merchandising initiatives.}
      \end{cvitems}
    }
  \vspace{3mm}
  \cventrynew
    {MINI-Q Digital Platform - Full-Stack Developer} % Organisation
    {Remote | July 2024 - Nov 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and deployed a full-stack healthcare web application digitising the MINI-Q questionnaire in collaboration with Auckland District Health Board clinicians (live: \href{https://miniq.nz}{\textcolor{blue!80!black}{\underline{miniq.nz}}}).}
        \item {Built React frontend (TypeScript), Express backend, and PostgreSQL database; deployed to AWS (EC2, RDS).}
      \end{cvitems}
    }
  \vspace{3mm}
  \cventrynew
    {EY Open Science Data Challenge Program - Machine Learning Mentee} % Organisation
    {Remote | Dec 2023 - March 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led team to top 20 global ranking; developed ML model (0.48 Mean Average Precision) for storm damage assessment using TensorFlow and scikit-learn.}
      \end{cvitems}
    }
  \vspace{3mm}
  \cventrynew
    {Biztech Society - PR and Tech Events Lead} % Organisation
    {Auckland, NZ | Jan 2024 - Nov 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Secured \$5000+ sponsorship from Microsoft and KPMG; led tech-focused rebrand driving 50+ student registrations.}
      \end{cvitems}
    }
\end{cventries2}
